---
title: "Final Project Proposal"
date: "11/7/2020"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  outout.width = "90%"
)
theme_set(theme_minimal()+theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour="viridis",
  ggplot2.continuous.fill="viridis"
)
scale_colour_discrete(scale_color_viridis_d())
scale_fill_discrete(scale_fill_viridis_d())
```

# Problem 1

```{r}
homocide_df = read_csv("homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city,state,sep="_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved",
    )
  ) %>% 
  select(city_state,resolved) %>% 
  filter(city_state != "Tulsa_AL")
```

Look at the data
```{r}
aggregate_df = homocide_df %>% 
  group_by(city_state) %>% 
  summarize(hom_total = n(),
            hom_unsolved = sum (resolved =="unsolved")
            )
```

prop.test for Baltimore
```{r}
prop.test(
  aggregate_df %>% filter(city_state =="Baltimore_MD") %>% pull(hom_unsolved),
  aggregate_df %>% filter(city_state =="Baltimore_MD") %>% pull(hom_total)
) %>% broom::tidy()

```


prop.test for every state
```{r}
result_df = aggregate_df %>% 
  mutate(
    prop_test=map2(.x = hom_unsolved, .y=hom_total, ~prop.test(x=.x, n=.y)),
    tidy_test = map(.x = prop_test, ~broom::tidy(.x))
  ) %>% 
  select(-prop_test) %>% 
  unnest(tidy_test) %>% 
  select(city_state, estimate, conf.low, conf.high)
```

```{r}
result_df %>% 
  mutate(city_state=fct_reorder(city_state,estimate)) %>% 
  ggplot(aes(x=city_state,y=estimate))+
  geom_point()+
  geom_errorbar(aes(ymin=conf.low,ymax=conf.high))+
  theme(axis.text.x= element_text(angle=90, vjust = 0.5, hjust=1))
```


#Question 2

Create a dataframe containing all file names
```{r}
path_df = 
  tibble(
    path = list.files(path = "lda_data")
  ) %>% 
  mutate(path = str_c("lda_data/",path)) %>% as.list()

ID_df =
  tibble(
    path = list.files(path = "lda_data")
  ) %>% 
  mutate(path = str_c("lda_data/",path))

```

Iterate over file name

```{r}
import_data = function(x){
  
  ID_df %>% filter(path==x) %>% 
    mutate(
        read_csv(x)
    )
}

lda_df= map(path_df$path,import_data) %>% bind_rows()

```

Data cleaning

```{r}
clean_df = lda_df %>% 
  separate(path,into = c("prefix","ID"),sep="/",) %>% 
  select(-prefix) %>% 
  separate(ID,into = c("arm","ID"),sep="_") %>% 
  separate(ID,into = c("arm_ID","suffix"),convert = TRUE) %>% 
  select(-suffix) %>% 
  mutate(
    ID = str_c(1:20)
  ) %>% 
  select(ID,everything())

time_data = unnest(clean_df$data)
clean_df = cbind(clean_df,time_data) %>% 
  select(ID:arm_ID,week_1:week_8)
```


spaghetti plot

```{r}
clean_df %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "value",
    names_prefix="week_"
  ) %>% 
    ggplot(aes(x=week,y=value,group=ID,color=arm))+
    geom_line()

```

Generally, the observational value was higher among experimental group than control group overtime. The observation value of subjects in experimental were shown to be increasing over time, while those in control group remained steady.












